%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%%
%%% 
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
%\defaultfontfeatures{Path = /usr/local/texlive/2022/texmf-dist/fonts/opentype/public/fontawesome}
%\usepackage{fontspec}
\usepackage{fontawesome,url}

\usepackage{etaremune}
\usepackage{enumitem}

\renewcommand*{\thesection}{\Roman{section}}
\renewcommand*{\thesubsection}{\Roman{subsection}}
\renewcommand*{\labelenumi}{[\labelprefix\theenumi]}

\definecolor{nice-purple}{HTML}{483d8b}
%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Rohit Zambre}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Nvidia Networking}
\def\myaddress{Seattle, WA}
\def\myemail{rzambre@nvidia.com}
\def\myweb{rohitzambre.com}
\def\mygithub{github.com/rzambre}
%\def\myphone{(515) 708-8387}
\def\myfax{(919) 660-5623}
\def\mytwitter{@rohitzambre}
\def\myversion{}
\def\myrevision{}


%\def\myaffiliation{AMD Research}
\def\myauthor{Rohit Zambre}
\date{} % not used (revision control instead)
\def\mykeywords{Rohit, Zambre, Rohit Zambre, Vita, CV, Resume, HPC}

%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
%\input{vc}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro}
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]{Unit-Medium}
\setmonofont[Mapping=tex-text,Scale=0.72]{Consolas} 

\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

\newfontface\addressblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro Medium Caption}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
%\pagestyle{kjh}
%\thispagestyle{kjhgit}


%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize 
 \href{https://www.nvidia.com/en-us/networking/}{Nvidia Networking},\\ \vspace{-0.05in} Seattle, \textsc{WA}, USA}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.3in}
  %\flushright \footnotesize  \addressblock \myphone \, \faPhone \\ 
  %\flushright \footnotesize  \addressblock \\ 
  \flushright \footnotesize 
  {\scriptsize  \texttt{\href{http://twitter.com/rohitzambre}{\mytwitter}} \, \faTwitter }  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{https://github.com/rzambre}{\mygithub}} \, \faGithub} \\
  {\scriptsize  \texttt{\href{https://www.rohitzambre.com}{\myweb}} \, \faGlobe}
\end{minipage}

\medskip

%% Name 
\noindent{\LARGE\scheader \textsc{Rohit Zambre}}
\reversemarginpar

\bigskip       

%% Education
\section{Education}

%\marginhead{\sffamily {{\vskip -0.23em} Education}}

%\noindent\emph{Princeton University \vspace{0.01in}}

\ind Ph.D., Computer Engineering, University of California, Irvine, 2020.

\ind \hspace{0.35in} \footnotesize Dissertation: \href{https://escholarship.org/uc/item/2g34n1hs}{Exascalable Communication for Modern Supercomputing}.
\newline Advisor: \href{https://hpcforge.eng.uci.edu/}{Aparna Chandramowlishwaran}.
\newline \href{https://www.sighpc.org/for-your-career/dissertation-award/2021-award-winner-rohit-zambre}{ACM SIGHPC Outstanding Doctoral Dissertation Award}.
\normalsize \vspace{0.05in}

\ind M.S., Computer Engineering, University of California, Irvine, 2017. 

\ind \hspace{0.35in} \footnotesize Thesis: \href{https://escholarship.org/content/qt1044v4n3/qt1044v4n3.pdf}{Adaptive Parallelism in Browsers}.
\normalsize \vspace{0.05in}

\ind B.S., Electrical Engineering, Iowa State University, 2015.

\ind \hspace{0.35in} \footnotesize Concentration: Computer Engineering.
\newline Magna Cum Laude.
\normalsize

\bigskip

\section{Appointments}

%% Research experience
% \medskip
\marginhead{\sffamily Research}

\ind Senior Software Architect, Nvidia Networking, 2022--present.
\vspace{0.01in}

\ind HPC Architecture Researcher, AMD Research, 2021--2022.
\vspace{0.01in}

\ind Graduate Student Researcher, University of California, Irvine, 2015--2020.
\vspace{0.01in}

\ind Visiting Student, Argonne National Laboratory, 2017--2020.
\vspace{0.01in}

\ind Research Intern, Arm Research, Summer 2018.
\vspace{0.01in}

\ind Research Aide, Argonne National Laboratory, Spring and Summer 2017.
\vspace{0.01in}
	
\ind Research Assistant, Mozilla Research, Summer 2016.

\bigskip

%% Engineering experience
% \medskip
\marginhead{\sffamily Engineering}

\ind Intern SSD Modeling Engineer, Micron Technology, Summer 2014.
\vspace{0.01in}

\ind NAND Product Engineering Intern, Micron Technology, Summer 2013.
\vspace{0.01in}

\bigskip

%% Teaching experience
% \medskip
\marginhead{\sffamily Teaching}

\ind Graduate Teaching Assistant, University of California, Irvine, Fall 2016.

\ind \hspace{0.35in} \footnotesize EECS 215: Design and Analysis of Algorithms.
\normalsize \vspace{0.05in}

\ind Peer Mentor, Iowa State University, 2012--2015.

\ind \hspace{0.35in} \footnotesize EE 185: Introduction to Electrical Engineering and Problem Solving.
\normalsize \vspace{0.05in}

\ind Undergraduate Teaching Assistant, Iowa State University, Fall 2013.

\ind \hspace{0.35in} \footnotesize CPR E 288: Embedded Systems.
\normalsize \vspace{0.05in}

\bigskip

\section{Honors \& awards}

%% Honors and awards
%\marginhead{\sffamily {\vskip 0.6em}Honors \newline \& awards}
%\medskip

\def\labelprefix{}
\begin{etaremune}

\item ACM SIGHPC Early Career Travel Grant to attend the ACM/IEEE Supercomputing Conference (SC), 2022.

\item AMD Research Spotlight Award, Quarter 1 2022.

\item ACM SIGHPC Outstanding Doctoral Dissertation Award, presented at the ACM/IEEE Supercomputing Conference (SC), 2021.

\ind \hspace{0.35in} \footnotesize Press: \href{https://www.sighpc.org/for-your-career/dissertation-award/2021-award-winner-rohit-zambre}{ACM SIGHPC announcement},
	\href{https://engineering.uci.edu/news/2021/7/zambre-wins-outstanding-doctoral-dissertation-award-supercomputing-communication}{UC Irvine news},
	\href{https://www.hpcwire.com/off-the-wire/acm-sighpc-announces-doctoral-dissertation-award-winner-rohit-zambre/}{HPCwire news}.
\normalsize

\item Contributor to an R\&D 100 Award winner: Unified Communication X (UCX), 2019.

\ind \hspace{0.35in} \footnotesize Press: \href{https://www.anl.gov/article/argonne-and-partners-take-home-nine-rd-100-awards-in-2019}{Argonne National Laboratory}
\normalsize

\item Best Poster Presentation Award, presented at the IEEE International Conference on Parallel and Distributed Systems (ICPADS), 2018.

\item Winner, People's Choice \& Judges' Choice, Graduate Research Symposium, UC Irvine, 2016

\item Tau Beta Pi Scholarship (\href{https://www.tbp.org/memb/ScholarArchives/ScholarReleases/2014ScholarshipRelease.pdf}{announcement}), 2014.

\item College of Engineering Scholarships, Iowa State University, 2014 and 2012.

	\ind \hspace{0.35in} \footnotesize Adolph Shane Scholarship, 2014.

	\vspace{-0.5em}
	\ind \hspace{0.35in} Arthur Edwin Zahller Endowed Scholarship, 2012.

\normalsize

\item Gold-level International Student Ambassador Scholarship, Iowa State University, 2011--2015.

\item Certificates of Merit, CBSE's\footnote{Central Board of Secondary Education.} All India Senior School Certificate Examination, 2011.

\ind \hspace{0.35in} \footnotesize Among top 0.1\% in Physics and Chemistry.

\vspace{-0.5em}
\ind \hspace{0.35in} Among top 1\% overall.

\normalsize

\item Certificates of Merit (among top 1/8\textsuperscript{th}) in all-India level tests conducted by third-party institutions before university education.

	\ind \hspace{0.35in} \footnotesize Gold medal (rank 25), CIPEL's\footnote{Central Institute for Proficiency in English Language} English Proficiency and General Knowledge Test, 2011.
	
	\vspace{-0.25em}
	\ind \hspace{0.35in} Rank 71, Bright Career Rohtak's Global Mathematics Talent Search, 2009.
	
	\vspace{-0.25em}
	\ind \hspace{0.35in} Gold medal (rank 13), CIPEL's English Proficiency and General Knowledge Test, 2003.

\normalsize

\end{etaremune}

\def\labelprefix{J}

%\newpage
\section{Refereed research}

%\subsection{Journal articles}
\marginhead{\sffamily {\vskip 0.5em}Journal\newline articles}
\medskip

\begin{etaremune}

\item \textbf{Rohit Zambre}, Damodar Sahasrabudhe, Hui Zhou, Martin Berzins, Aparna Chandramowlishwaran, Pavan Balaji. ``\href{https://doi.org/10.1109/TPDS.2021.3075157}{Logically Parallel Communication for Fast MPI+Threads Applications}.'' \emph{IEEE Transactions on Parallel and Distributed Systems (TPDS)}, April 2021.

\item Damodar Sahasrabudhe, \textbf{Rohit Zambre}, Aparna Chandramowlishwaran, Martin Berzins. ``\href{https://doi.org/10.1016/j.jocs.2020.101279}{Optimizing the Hypre solver for manycore and GPU architectures}.'' \emph{Elsevier Journal of Computational Science (JCS)}, December 2020.

\end{etaremune}

%\marginhead{\sffamily {\vskip 0.35em} Publications}
%\medskip

 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

%\end{revnumerate}
\bigskip
%\newpage

%\subsection{Conference proceedings}
\marginhead{\sffamily {\vskip 0.1em}Conference\newline proceedings}
%\medskip
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

\def\labelprefix{C}

\begin{etaremune}

\item \textbf{Rohit Zambre}, Aparna Chandramowlishwaran. ``\href{https://dl.acm.org/doi/abs/10.5555/3571885.3571987}{Lessons Learned on MPI+Threads Communication}.'' \emph{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, Dallas, TX, USA, November 2022.

\item \textbf{Rohit Zambre}, Aparna Chandramowlishwaran, Pavan Balaji. ``\href{https://doi.org/10.1145/3392717.3392773}{How I Learned to Stop Worrying About User-Visible Endpoints and Love MPI}.'' \emph{34th ACM International Conference of Supercomputing (ICS)}, Worldwide online event, June 2020.

\item \textbf{Rohit Zambre}, Megan Grodowitz, Aparna Chandramowlishwaran, Pavel Shamis. ``\href{https://doi.org/10.1145/3337821.3337910}{Breaking Band: A Breakdown of High-Performance Communication}.'' \emph{48th ACM International Conference on Parallel Processing (ICPP)}, Kyoto, Japan, August 2019.

\item \textbf{Rohit Zambre}, Aparna Chandramowlishwaran, Pavan Balaji. ``\href{https://doi.org/10.1109/PADSW.2018.8645059}{Scalable Communication Endpoints for MPI+Threads Applications}.'' \emph{24th IEEE International Conference on Parallel and Distributed Systems (ICPADS)}, Sentosa, Singapore, December 2018.

\item \textbf{Rohit Zambre}, Lars Bergstrom, Laleh Beni, Aparna Chandramowlishwaran. ``\href{https://doi.org/10.1109/HiPC.2016.013}{Parallel Performance-Energy Predictive Modeling of Browsers: Case Study of Servo}''. \emph{23rd IEEE International Conference on High Performance Computing, Data, and Analytics (HiPC)}, Hyderabad, India, December 2016.
 
\end{etaremune}
% %\end{revnumerate}
%\bigskip
%\pagebreak

%\subsection{Posters}
\marginhead{\sffamily {\vskip 0.5em}Posters}
\medskip

\def\labelprefix{P}

\begin{etaremune}

\item \textbf{Rohit Zambre}. ``The Coming of Age of Multithreaded High-Performance Communication.'' Doctoral Showcase at the \emph{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC) }, Atlanta, GA, USA, November 2020.

\item \textbf{Rohit Zambre}, Aparna Chandramowlishwaran, Pavan Balaji. ``Scalable Communication Endpoints for MPI+Threads Applications.'' \emph{IEEE International Conference on Parallel and Distributed System (ICPADS)}, Sentosa, Singapore, December 2018. \textbf{\textcolor{nice-purple}{Best Poster Presentation Award}}.

\item \textbf{Rohit Zambre}, Abdelhalim Amer, Aparna Chandramowlishwaran, Pavan Balaji. ``Evaluating Multiple Endpoints for MPI with libibverbs.'' \emph{24th ACM European MPI Users' Group Meeting (EuroMPI/USA)}, Chicago, IL, USA, September 2017.

\item \textbf{Rohit Zambre}, Lars Bergstrom, Laleh Beni, Aparna Chandramowlishwaran. ``Parallel Performance-Energy Predictive Modeling of Browsers: Case Study of Servo.'' \emph{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, Salt Lake City, UT, USA, November 2016.

\end{etaremune}

\section{Presentations}

\marginhead{\sffamily {\vskip 0.5em}Tutorials}
\medskip

\ind ``Introduction to MPI.'' HPC-AI Advisory Council 10th RDMA Programming Competition, August 2022.
\vspace{0.01in}

\marginhead{\sffamily {\vskip 0.5em}Invited talks}
\medskip

\ind ``Exascalable Communication for Modern Supercomputing.'' Pacific Northwest National Laboratory, October 2021.
\vspace{0.01in}

\ind ``The Coming of Age of Multithreaded High-Performance Communication.'' AMD Research, September 2020.
\vspace{0.01in}

\ind ``Levaraging SC to Learn High-Performance Communication.'' The 6th Workshop on Best Practices for HPC Tranining and Education (BPHTE), November 2019.
\vspace{0.01in}

\ind ``Scalable Communication Endpoints for MPI+Threads Applications.'' Arm Research, September 2018.

\newpage

\marginhead{\sffamily {\vskip 0.5em}Conferences}
\medskip

\ind ``Lessons Learned on MPI+Threads Communication.'' ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC), Dallas, TX, USA, November 2022.
\vspace{0.01in}

\ind ``The Coming of Age of Multithreaded High-Performance Communication.'' ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC), Online, November 2020.
\vspace{0.01in}

\ind ``How I Learned to Stop Worrying About User-Visible Endpoints and Love MPI.'' ACM International Conference on Supercomputing (ICS), Online, June 2020.
\vspace{0.01in}

\ind ``Breaking Band: A Breakdown of High-Performance Communication.'' ACM International Conference on Parallel Processing (ICPP), Kyoto, Japan, August 2019. 
\vspace{0.01in}
 
\ind ``Scalable Communication Endpoints for MPI+Threads Applications.'' IEEE International Conference on Parallel and Distributed Systems (ICPADS), Sentosa, Singapore, December 2018. 
\vspace{0.01in}

\ind ``Parallel Performance-Energy Predictive Modeling of Browsers: Case Study of Servo.'' IEEE International Conference on High Performance Computing, Data, and Analytics (HiPC), Hyderabad, India, December 2016. 

%\newpage

\marginhead{\sffamily {\vskip 0.5em}Other}
\medskip

\ind ``Parallel Performance-Energy Predictive Modeling of Browsers: Case Study of Servo.'' UCI Graduate Research Symposium, Irvine, CA, USA, April 2016. \textbf{\textcolor{nice-purple}{Winner, People's Choice \& Judge's Choice.}}

%\end{revnumerate}

\bigskip

\section{Service}
%\newpage

\marginhead{\sffamily {\vskip 0.5em}Peer\newline reviewing}
\medskip

\ind Reproducibility challenge committee, \href{https://sc23.supercomputing.org/}{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, 2023.
\vspace{0.01in}

\ind Program committee, Programming Models, Compilers, and Runtime Systems track, \href{https://www.ipdps.org/ipdps2023}{37th IEEE International Parallel and Distributed Processing Symposium (IPDPS)}, 2023.
\vspace{0.01in}

\ind Program committee, \href{https://www.openfabrics.org/2023-ofa-workshop/}{19th OpenFabrics Alliance (OFA) Workshop}, 2023.
\vspace{0.01in}

\ind Student volunteer applications, \href{https://sc22.supercomputing.org/}{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, 2022.
\vspace{0.01in}

\ind Program committee, \href{https://www.openfabrics.org/2022-ofa-workshop/}{18th OpenFabrics Alliance (OFA) Workshop}, 2022.
\vspace{0.01in}

\ind Research posters, \href{https://www.isc-hpc.com/isc-committees.html}{International Supercomputing Conference (ISC)}, 2022.
\vspace{0.01in}

\ind Program committee, Programming Models and Systems Software track, \href{http://sighpc.ipsj.or.jp/HPCAsia2022/}{5th International Conference on High Performance Computing (HPC Asia)}, 2022.
\vspace{0.01in}

\ind Research posters, \href{https://www.isc-hpc.com/isc-committees.html}{International Supercomputing Conference (ISC)}, 2021.
\vspace{0.01in}

\ind Student volunteer applications, \href{https://sc20.supercomputing.org/}{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, 2020.

\ind Student volunteer applications, \href{https://sc19.supercomputing.org/}{ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, 2019.

\marginhead{\sffamily {\vskip 0.5em}Conference\newline organization}
\medskip

\ind Program Co-Chair, \href{https://hoti.org/}{30th IEEE Hot Interconnects Symposium (HotI)}, 2023.
%\vspace{0.01in}

\ind Program Co-Chair, \href{https://hoti.org/}{29th IEEE Hot Interconnects Symposium (HotI)}, 2022.
%\vspace{0.01in}

\ind Online Conference Co-Chair, \href{https://hoti.org/}{29th IEEE Hot Interconnects Symposium (HotI)}, 2022.
%\vspace{0.01in}

\ind Web Chair, \href{https://hoti.org/}{28th IEEE Hot Interconnects Symposium (HotI)}, 2021.
%\vspace{0.01in}

\ind Lead Student Volunteer, \href{https://sc20.supercomputing.org/2020/07/07/eighteen-sc20-lead-student-volunteers-announced/}{ACM/IEEE ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC)}, 2020 and 2019.
%\vspace{0.01in}

\ind Web Chair, \href{https://www.mcs.anl.gov/events/workshops/ashes/2019/organizers.php}{9th IEEE International Workshop on Accelerators and Hybrid Exascale Systems (AsHES)}, 2019.
%\vspace{0.01in}

\ind Student Volunteer, ACM/IEEE International Conference for High Performance Computing, Networking, Storage and Analysis (SC), 2018, 2017 and 2016.

\marginhead{\sffamily {\vskip 0.5em}Student\newline  organization}
\medskip

\ind Engineering council member, Associated Graduate Students, Univeristy of California, Irvine, 2016--2017.

\ind President and Treasurer, Indian Students' Association, Iowa State University, 2012--2014.

\end{document}
